Spectral Deferred Corrections Scheme for Low Mach Number Flows

### 2020-01-01 MAESTROeX_II/paper.tex
add ref

{\bf Step 2C:} ({\it Advance thermodynamic variables})\\ \\
Define $Q_{\rho X_k}^{(0)}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{(0)}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{\rho h}^{\rm lagged}$ term.  Use {\tt VODE} to integrate (\ref{eq:species}) and (\ref{eq:enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,(0)}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{(0)} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{(0)} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{(0)}$ and $I_{\rho h}^{(0)}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the corrector step.  In our first implementation, we are predicting $\rho X_k$ and $\rho h$, in which case we define:
\begin{eqnarray}
I_{\rho X_k}^{(0)} &=& \frac{(\rho X_k)^{n+1,(0)} - (\rho X_k)^n}{\Delta t} - Q_{\rho X_k}^{(0)}\\
I_{\rho h}^{(0)} &=& \frac{(\rho h)^{n+1,(0)} - (\rho h)^n}{\Delta t} - Q_{\rho h}^{(0)}.
\end{eqnarray}

>>>>

{\bf Step 2C:} ({\it Advance thermodynamic variables})\\ \\
Define $Q_{\rho X_k}^{(0)}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{(0)}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{\rho h}^{\rm lagged}$ term.  Use {\tt VODE} \citep{vode} to integrate (\ref{eq:species}) and (\ref{eq:enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,(0)}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{(0)} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{(0)} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{(0)}$ and $I_{\rho h}^{(0)}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the corrector step.  In our first implementation, we are predicting $\rho X_k$ and $\rho h$, in which case we define:
\begin{eqnarray}
I_{\rho X_k}^{(0)} &=& \frac{(\rho X_k)^{n+1,(0)} - (\rho X_k)^n}{\Delta t} - Q_{\rho X_k}^{(0)}\\
I_{\rho h}^{(0)} &=& \frac{(\rho h)^{n+1,(0)} - (\rho h)^n}{\Delta t} - Q_{\rho h}^{(0)}.
\end{eqnarray}
